```{r}
#install.packages(ggplot2)
#install.packages(corrplot)
library(ggplot2)
library(corrplot)
```

```{r}
path="../datasets/"

```

```{r}
#paths to six random countries 
path1="normalized-age-data-waf/us_waf.csv"
path2="normalized-age-data-waf/pa_waf.csv"
path3="normalized-age-data-waf/ph_waf.csv"
path4="normalized-age-data-waf/de_waf.csv"
path5="normalized-age-data-waf/es_waf.csv"
path6="normalized-age-data-waf/fr_waf.csv"


```

```{r}
#reading the files into data frames
us = read.csv(paste0(path,path1))
pa = read.csv(paste0(path,path2))
ph = read.csv(paste0(path,path3))
de = read.csv(paste0(path,path4))
es = read.csv(paste0(path,path5))
fr = read.csv(paste0(path,path6))

```

```{r}
#making the data a Date type
us$Date=paste0(us$Year,'-',us$Month,'-',us$Day)
us$Date=as.Date(us$Date)

#takes the subset of the dataset that contains only the songs mentioned in the list
us_song=us[us$Track.Name %in% c("Sunflower - Spider-Man: Into the Spider-Verse", "Wow.") ,]
us_song1=us[us$Track.Name %in% c("Sunflower - Spider-Man: Into the Spider-Verse", "7 rings") ,]

#range of dates to plot for
min <- as.Date("2019-1-1")
max <- as.Date("2019-6-30")

#plotting the inverse position of the song against time 
ggplot(us_song, aes(x = us_song$Date, y = (100-us_song$Position)/100)) + 
  geom_line(aes(color = us_song$Track.Name), size = 1) +
  
  theme_minimal()+scale_x_date(date_labels = "%b/%Y",limits = c(min, max))+xlab("Time") +
  ylab("Popularity") +
  ggtitle("Popularity vs. Time")

ggplot(us_song1, aes(x = us_song1$Age.on.Chart, y = (100-us_song1$Position)/100)) + 
  geom_line(aes(color = us_song1$Track.Name), size = 1) +
  
  theme_minimal()+
  ylab("Popularity") +
  ggtitle("Popularity vs. Age of song")


```

Graph 1 shows that the popularity of a song goes down with time(Example taken of 2 songs). However in graph 1  we notice that on 8th febrauary 2019 both the songs popularity goes down . Why is this?

One 8th february 2019 Ariana Grande relased an album "Thank you next which contisted of 10 songs . hence on this day popularity of other songs went down".

From the next graph between sunflower and 7 rings we can see that the Ariana Grande's Album  dint do so well .So it decreased ,where as sunflower did well over time.



SEEING THE VALUE SPREAD OF DIFFRENT FEATURES OF POPULAR SONGS IN DIFFRENT COUNTRIES





```{r}

#getting attributes to subset dataframe plot for boxplot
x=data.frame(us$danceability, pa$danceability,ph$danceability,de$danceability,es$danceability,fr$danceability)
x1=data.frame(us$acousticness, pa$acousticness,ph$acousticness,de$acousticness,es$acousticness,fr$acousticness)

x2=data.frame(us$energy, pa$energy,ph$energy,de$energy,es$energy,fr$energy)

x3=data.frame(us$speechiness,pa$speechiness,ph$speechiness,de$speechiness,es$speechiness,fr$speechiness)

x4=data.frame(us$liveness,pa$liveness,ph$liveness,de$liveness,es$liveness,fr$liveness)

x5=data.frame(us$norm_tempo,pa$norm_tempo,ph$norm_tempo,de$norm_tempo,es$norm_tempo,fr$norm_tempo)

```

```{r}

#plotting the boxplots

par(mfrow=c(2,2))
boxplot(x,names = c("us", "pa", "ph","de","es","fr"),
col = c("orange"),
border = "brown",xlab="Country",
ylab="Dancability")

boxplot(x1,names = c("us", "pa", "ph","de","es","fr"),col = c("light blue"),xlab="Country",
ylab="Acousticness")

boxplot(x2,names = c("us", "pa", "ph","de","es","fr"),col = c("light green"),xlab="Country",
ylab="Energy")

boxplot(x3,names = c("us", "pa", "ph","de","es","fr"),col = c("yellow"),xlab="Country",
ylab="Speechiness")

boxplot(x5,names = c("us", "pa", "ph","de","es","fr"),col = c("grey"),xlab="Country",
ylab="tempo")

```

From the above graphs we can conclude that popular songs have:
1) High dancability
2) Low acoustics
3) Medium energy (Slightly on higher side)
4) Low speechiness
5) Medium Tempo (Slightly on lower side)

```{r}

#plotting the correlogram between select attributes
us_cor=data.frame(us$energy,us$danceability,us$speechiness,us$norm_loudness,us$norm_tempo,us$norm_duration_min,us$acousticness)
par(mfrow=c(1,1))
m=cor(us_cor)

corrplot(m, method="color")

```
With in a country the few attributes have correlation
1) Energy and Loudness have a positive correlation as expected
2) Energy and acousticness have negative correlation



```{r}


#energy for 1st position songs for a list of countries 
par(mfrow=c(1,2))
energy=data.frame(us$energy[us$Position == 1],pa$energy[pa$Position == 1],ph$energy[ph$Position == 1],es$energy[es$Position == 1],de$energy[de$Position == 1],fr$energy[fr$Position == 1])
m1=cor(energy)

#row and column names
rownames(m1) <- c("US", "PA","PH","ES","DE","FR")
colnames(m1) <- c("US", "PA","PH","ES","DE","FR")

#plotting correlogram for energy
corrplot(m1, method="shade",title="ENERGY")

#speechiness for 1st position songs for a list of countries 
sp=data.frame(us$speechiness[us$Position == 1],pa$speechiness[pa$Position == 1],ph$speechiness[ph$Position == 1],es$speechiness[es$Position == 1],de$speechiness[de$Position == 1],fr$speechiness[fr$Position == 1])
m2=cor(sp)

#row and column names
rownames(m2) <- c("US", "PA","PH","ES","DE","FR")
colnames(m2) <- c("US", "PA","PH","ES","DE","FR")

#plotting correlogram for Speechiness
corrplot(m2, method="shade",title="SPEECHINESS")
```

Note that there is no colrelation between the attributes of diffrent countries


```{r}
#plots the danceability and energy against time

par(mfrow=c(1,2))
d<-data.frame(us$Date,us$danceability)
ag=aggregate(us$danceability ~ us$Date, d, mean)


min <- as.Date("2019-1-1")
max <- as.Date("2019-6-30")
ggplot(ag, aes(x = ag$`us$Date`, y =ag$`us$danceability`) )+ 
  geom_line(aes(color = "Danceability"), size = 1) +
  
  theme_minimal()+scale_x_date(date_labels = "%b/%Y",limits = c(min, max))+xlab("Time") +
  ylab("Danceability") +
  ggtitle("Danceability of popular songs vs. Time")
d<-data.frame(us$Date,us$energy)
ag=aggregate(us$energy ~ us$Date, d, mean)
ggplot(ag, aes(x = ag$`us$Date`, y =ag$`us$energy`) )+ 
  geom_line(aes(color = "Energy"), size = 1) +
  
  theme_minimal()+scale_x_date(date_labels = "%b/%Y",limits = c(min, max))+xlab("Time") +
  ylab("Energy") +
  ggtitle("Energy of popular songs vs. Time")



```

